---
title: "ANLY 530 Group Assignment (Laboratory 1)"
author:
- "Josseline Betio"
- "Akpany Benjamin Ebby"
- "Yajun Wang"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    highlight: zenburn
comment: Rmd Document with Markdown + Embedded R Code
---

---

#### Document as of `r Sys.Date()`

```{r setup, include=FALSE, purl=FALSE, eval=TRUE}

source('R/ANLY530_Laboratory1_Helper.R')

```

```{r echo=FALSE}

library(knitr)
library(kableExtra)
read_chunk('R/ANLY530_Laboratory1_Chunks.R')

```

Some helper functions do exists to support the code snippets below such as: ```fullFilePath```

---

# Method #1. Tree-based classification


```{r loadLibraries, echo=FALSE, message=FALSE, warning=FALSE}
```

Let us start by [Loading the Data Sheets]

```{r loadSheets, echo=FALSE, message=FALSE, warning=FALSE}
```

## [Step 1: Collecting the data]

```{r method1Step1CollectingData, echo=FALSE, message=FALSE, warning=FALSE}
```

## [Step 2: Exploring the data]

```{r method1Step2ExploringData, echo=FALSE, message=FALSE, warning=FALSE}
```

## [Step 3: Training a model on the data]

```{r method1Step3ModelTraining, echo=FALSE, message=FALSE, warning=FALSE}
```

## [Step 4: Evaluating Model Performance]

```{r method1PerformanceEvaluation, echo=FALSE, message=FALSE, warning=FALSE}
```

## Method 1 Confusion Table

```{r method1ConfusionTable, echo=FALSE, message=FALSE, warning=FALSE}
```

# Method #2. Support vector machines

## [Method 2 Step 1: Collecting the data]

```{r method2Step1CollectingData, echo=FALSE, message=FALSE, warning=FALSE}
```

## [Method 2 Step 2: Preparing the Data]

```{r method2Step2PreparinggData, echo=FALSE, message=FALSE, warning=FALSE}
```

## [Method 2 Step 3: Training a Model on the Data]

```{r method2Step3ModelTraining, echo=FALSE, message=FALSE, warning=FALSE}
```

## [Method 2 Step 4: Evaluating Model Performance]

```{r method2PerformanceEvaluation, echo=FALSE, message=FALSE, warning=FALSE}
```

## [Method 2 Agreement Table]

```{r method2AgreementTable, echo=FALSE, message=FALSE, warning=FALSE}
```

# Method #3. Adding regression to trees

## [Method 3 Step 1: Collecting the Data]

```{r method3Step1CollectingData, echo=FALSE, message=FALSE, warning=FALSE}
```

## [Method 3 Step 2: Exploring and Preparing the Data]


```{r method3Step2ExploringPreparingData, echo=FALSE, message=FALSE, warning=FALSE}
```

## [Method 3 Step 3: Training a Model on the Data]


```{r method3Step3ModelTraining, echo=FALSE, message=FALSE, warning=FALSE}
```

## [Method 3 Step 4: Evaluating Model Performance]

```{r method3Step4PerformanceEvaluation, echo=FALSE, message=FALSE, warning=FALSE}
```

---

# Appendix

### Required Libraries

```{r installLibraries, eval=FALSE}
```

```{r loadLibraries, eval=FALSE}
```

### Helper Functions

```{r helperFunctions, eval=FALSE}
```

### Loading the Data Sheets

```{r loadSheets, eval=FALSE}
```

### Method 1 Step 1: Collecting the data

```{r method1Step1CollectingData, eval=FALSE}
```

### Method 1 Step 2: Exploring the data

```{r method1Step2ExploringData, eval=FALSE}
```

### Method 1 Step 3: Training a model on the data

```{r method1Step3ModelTraining, eval=FALSE}
```

### Method 1 Step 4: Evaluating Model Performance

```{r method1PerformanceEvaluation, eval=FALSE}
```

### Method 2 Step 1: Collecting the data

```{r method2Step1CollectingData, eval=FALSE}
```

### Method 2 Step 2: Preparing the Data

```{r method2Step2PreparinggData, eval=FALSE}
```

### Method 2 Step 3: Training a Model on the Data

```{r method2Step3ModelTraining, eval=FALSE}
```

### Method 2 Step 4: Evaluating Model Performance

```{r method2PerformanceEvaluation, eval=FALSE}
```

```{r method2AgreementTable, eval=FALSE}
```

### Method 3 Step 1: Collecting the Data

```{r method3Step1CollectingData, eval=FALSE}
```

### Method 3 Step 2: Exploring and Preparing the Data


```{r method3Step2ExploringPreparingData, eval=FALSE}
```

### Method 3 Step 3: Training a Model on the Data

```{r method3Step3ModelTraining, eval=FALSE}
```

### Method 3 Step 4: Evaluating Model Performance

```{r method3Step4PerformanceEvaluation, eval=FALSE}
```

## References

